A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-07-06 doc/popl2013/intro.tex
Moving one of the constraints in listing 2

% The tree example with partitioning and tree reversal
\begin{lstlisting}[float={t},label={lst:treereverse},caption={Tree Partitioning and Reversal Example}]
type tree<rl,rls,rt> = rr[rll, rlr, rtl, rtr] 
                       < list<rl>@rls, < tree<rl,rll,rtl>@rtl, tree<rl,rlr,rtr>@rtr > >
     		       where rll #$\le$# rls and rlr #$\le$# rls and rll #$*$# rlr and 
                                  rtl #$\le$# rt and rtr #$\le$# rt and rtl #$*$# rtr and rls #$\le$# rl

>>>>

% The tree example with partitioning and tree reversal
\begin{lstlisting}[float={t},label={lst:treereverse},caption={Tree Partitioning and Reversal Example}]
type tree<rl,rls,rt> = rr[rll, rlr, rtl, rtr] 
                       < list<rl>@rls, < tree<rl,rll,rtl>@rtl, tree<rl,rlr,rtr>@rtr > >
     		       where rll #$\le$# rls and rlr #$\le$# rls and rll #$*$# rlr and rls #$\le$# rl and
                                  rtl #$\le$# rt and rtr #$\le$# rt and rtl #$*$# rtr
